---
title: "LinearModel2"
author: "Irene"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

## Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM regression

```{r}
plot(SIMS~ARM,data=data)
```

The greater the pounds of arm force(ARM), the greater the simulation(SIMS)


```{r}
cor(SIMS~ARM,data=data)
```
This number is the correlation between SIMS and ARM force. Correlation is a measure of the linear association between the two variables.


```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation is -4.095160 +  0.054563 * ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

The scatter plot shows the blue line which is best linear fitto predict what what an average SIMS response would be for any ARM strength.
